\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{DevOps - Final Report\\
  \large Group I
}
\author{
Anders Latif (alat@itu.dk)\\
Ivar Cmrecak (ivcm@itu.dk)\\
Mads Meinert Andersen (mmea@itu.dk) \\
Mikkel Rahlff Berggreen (mirb@itu.dk)\\ 
Nedas Surkus (nesu@itu.dk)\\
}
\date{May 2023}

\begin{document}

\maketitle


\pagebreak


\section{System's Perspective} 



\subsection{Design and architecture of the system}

Design and architecture of your ITU-MiniTwit systems

\subsection{Dependencies of the system}
All dependencies of your ITU-MiniTwit systems on all levels of abstraction and development stages.
That is, list and briefly describe all technologies and tools you applied and depend on.
\subsection{Subsystem interactions}

\subsection{State of the system}

All dependencies of your ITU-MiniTwit systems on all levels of abstraction and development stages.
That is, list and briefly describe all technologies and tools you applied and depend on.

\subsection{Licences}
Finally, describe briefly, if the license that you have chosen for your project is actually compatible with the licenses of all your direct dependencies.

\subsection{Weekly tasks}
MSc students remember to argue for the choice of technologies and decisions for at least all cases for which we asked you to do so in the tasks at the end of each session.

\section{Process' perspective}

\subsection{Developer interaction}

\subsection{Team Organisation}


\subsection{Stages and tools utilized in CI/CD chains}
That is, including deployment and release of your systems.

\subsection{Organization of the repository}

That is, either the structure of of mono-repository or organization of artifacts across repositories.
In essence, it has to be be clear what is stored where and why.

\subsection{Branching strategy}

\subsection{Development process and tools supporting it}

For example, how did you use issues, Kanban boards, etc. to organize open tasks

\subsection{Monitoring}



\subsection{Logging}

\subsection{Security Assessment}

\subsection{Scaling and Load balancing}


\subsection{Other Artifacts}
In case you have used AI-assistants for writing code during your project or to write the report:
Explain which system(s) you used during the project.
Reflect how it supported/hindered your process.
In essence it has to be clear how code or other artifacts come from idea into the running system and everything that happens on the way.


\section{Lessons Learned Perspective}

\subsection{Issues and lessons learned}
Describe the biggest issues, how you solved them, and which are major lessons learned with regards to:

evolution and refactoring operation, and maintenance of your ITU-MiniTwit systems. Link back to respective commit messages, issues, tickets, etc. to illustrate these.
\subsection{Reflection}

Also reflect and describe what was the "DevOps" style of your work. For example, what did you do differently to previous development projects and how did it work?


\end{document}
